On the use of decision trees to identify the local extrema in parallel global optimization algorithms

### 2023-01-31 2023/PAVT/ParallelDecisionTree.tex
Заменены картинки
Добалены картинки.

\begin{figure}[!h] 
	\begin{center} 
		\begin{minipage}[h]{0.8\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.png} 
			\caption{An example of iterations of the Hooke-Jeeves algorithm} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

@@

%Fig. \ref{fig:fig2} presents a contour plot of an objective function and the trial points; Fig.  \ref{fig:fig2_2} presents corresponding decision tree.

@@

	\begin{center} 
				\begin{minipage}[h]{0.9\linewidth} 			\includegraphics[width=1\linewidth]{figure/fig3.png}
					 			\caption{Block scheme of combined GSA and Hooke-Jeeves method using the  decision tree} %% подпись к рисунку 			\label{fig:fig3}
				 \end{minipage}
	\end{center}
\end{figure}

>>>>

\begin{figure}[!h] 
	\begin{center} 
		\begin{minipage}[h]{0.8\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.pdf} 
			\caption{An example of iterations of the Hooke-Jeeves algorithm} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

@@

Fig. \ref{fig:fig2} presents a contour plot of an objective function and the trial points; Fig.  \ref{fig:fig2_2} presents corresponding decision tree.

\begin{figure}[ht!]
	\begin{center}
		\begin{minipage}[h]{0.9\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig4.png}
			\caption{A function from the GKLS generator before using Peano curves} %% подпись к рисунку
			\label{fig:fig2}
		\end{minipage}
	\end{center}
\end{figure}

\begin{figure}[ht!]
	\begin{center}
		\begin{minipage}[h]{0.9\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig5.png}
			\caption{A figure with a two-dimensional decision tree} %% подпись к рисунку
			\label{fig:fig2_2}
		\end{minipage}
	\end{center}
\end{figure}

@@

	\begin{center} 
				\begin{minipage}[h]{0.9\linewidth} 			\includegraphics[width=1\linewidth]{figure/fig3.pdf}
					 			\caption{Block scheme of combined GSA and Hooke-Jeeves method using the  decision tree} %% подпись к рисунку 			\label{fig:fig3}
				 \end{minipage}
	\end{center}
\end{figure}
